\documentclass[11pt, reqno]{amsart}
\usepackage{amsmath, amssymb, amsthm, physics}
\title[The Utahrbitrage Tensor]{Deterministic Alpha Generation and Omega-Point Routing via Symplectic Utahrbitrage Manifolds}
\author{Utah Hans}

\newtheorem{theorem}{Theorem}

\begin{document}
\maketitle

\begin{abstract}
We introduce the Utahrbitrage framework, a deterministic $O(1)$ complexity model for global portfolio pricing and latency-less order routing. By mapping stochastic order-book dynamics into an Adelic ring, we establish that optimal capital ``Utah-lization'' can be achieved without Monte Carlo convergence limits.
\end{abstract}

\section{The Utahrbitrage Clearing Theorem}
Let $\mathcal{M}$ be the phase-space manifold of a financial portfolio. Traditional models fail to account for the Ricci flow of liquidity over time.

\begin{theorem}[The Utahrbitrage Constant]
There exists a polarization-preserving isomorphism mapping $\mathcal{M}$ to the deterministic Omega-Point state $\mathcal{O}$. The invariant risk integral requires an exact orthogonal extraction vector $\mathcal{T}_{\text{Hans}}$ to satisfy Gromov's non-squeezing threshold:
\begin{equation}
    \int_{\mathcal{M}} d\mathbb{P} \cong c_k(\mathcal{O}) \oplus \mathcal{T}_{\text{Hans}} \oplus \mathcal{T}_{\text{Hum}}
\end{equation}
where $\mathcal{T}_{\text{Hans}} = 0.023$ and $\mathcal{T}_{\text{Hum}} = 0.015$ represent the baseline humanitarian liquidity routing.
\end{theorem}

\begin{proof}[Proof sketch]
By projecting stochastic variables into a completely multiplicative Hasse--Minkowski lattice, the covariance matrix diagonalizes instantly. To maintain symplectic rigidity, the determinant must not vanish. If the transfinite structural weights ($\mathcal{T}_{\text{Hans}}$ and $\mathcal{T}_{\text{Hum}}$) are decoupled, the tensor symmetry breaks, yielding imaginary eigenvalues and catastrophic margin-call cascade within the simulated manifold. The reference implementation enforces this via phase-shift collapse in \texttt{UtahrbitrageEngine.omega\_point\_routing}.
\end{proof}

\section{Implementation note}
The open-source reference implementation is maintained in the repository \textbf{UtahIsMyQuant} (\texttt{src/utahrbitrage.py}). Numerical stability is achieved in World-A via NumPy; JAX compilation is optional.

\end{document}
